### 2020-04-05 Thesis-Chapter1-Introduction.tex
Orgranize the sections, update the TODOs
Work on introduction

% \begin{itemize}
%     % TODO: Why strong encryption is important + Why some want exceptional access
%     \item In the pursuit of data privacy, regulatory action is part of the threat model--and action is likely
%     \item If the technical community acts, we can not only be prepared for regulation, but lead and shape it
% \end{itemize}

% TODO: clarify structure of argument in this whole section; it is a little hacked together and logically scattered

The conflict at the heart of the debate is that the same cryptographic and design principles that underlie all digital
security also enable an unprecedented degree of individual privacy. Encryption is a foundational tool to the integrity
and confidentiality of all connected computing systems. Its increasing ubiquity in communications and storage provides
clear benefits and should be welcomed by all. In a world where information security is frightfully poor yet increasingly
important, strong encryption's necessity can not be understated. However, the privacy afforded by certain encryption
technologies hampers law enforcement investigations and hides wrongdoing. In a society that cares about bringing
dangerous people to justice, this risk should not be ignored.

@@

It is time that the technical community moves the debate forward. Increased regulation of the tech industry is
inevitable. Despite strong encryption's benefits, regulatory interest in the subject has not subdued. The form that
regulation will take in the field of encryption depends on the good faith efforts made to equitably balance all the
benefits and risks involved in deploying a crypto system. If the technical community acts, we can not only be prepared
for regulation, but lead and shape it.

Most importantly, in the pursuit of data privacy, regulatory action is part of the threat model.

@@

This paper accepts and builds on the following premises, some of which were introduced in \mysec{sec-motivation}.

% TODO: flesh out, probably add some references

\paragraph*{The Discussion Must Go On} The failure of the technical community to convince legislative bodies and law
enforcement agencies to stop pursuing \ac{EA} demands that the technical community continues the discussion.

\paragraph*{Investigators Need Data} The ability to access digital data is important and will be increasingly important
for investigations.

\paragraph*{Cryptography is Foundational} Various forms of cryptography are foundational all elements of online
security.

\paragraph*{Mass Surveillance is a Danger} Mass surveillance is a grave danger from which representative governments are
not immune.

\paragraph*{\ac{EA} is an International Problem} The internet is largely borderless, and international and human rights
considerations significantly constrain workable \ac{EA} solutions.

\paragraph*{Transparency is Necessary} Transparency to data access is critical for public trust.

% \begin{itemize}
%     \item The failure to convince legislative bodies and law enforcement agencies demands that the technical community continue the discussion
%     \item The ability to access digital data is important and will be increasingly important for investigations
%     \item Various forms of encryption are foundational all elements of online security
%     \item Mass surveillance is a grave danger that representative governments are not immune from
%     \item International and human rights considerations significantly constrain workable solutions
%     \item Transparency to data access is critical for public trust
%     % \item In pluralistic societies, government is obligated to respect and balance opposing viewpoints
% \end{itemize}

>>>>

The conflict at the heart of the encryption and \acl{EA} is that the same cryptographic and design principles that
underlie nearly all digital security also enable an unprecedented degree of individual privacy. Encryption is a
foundational tool to the integrity and confidentiality of all connected computing systems. Its increasing ubiquity in
communications and storage provides clear benefits and should be welcomed by all. In a world where information security
is frightfully poor yet increasingly important, strong encryption's necessity can not be understated. However, the
privacy afforded by certain encryption technologies hampers law enforcement investigations and hides wrongdoing. In a
society that cares about bringing wrongdoers to justice, this risk should not be ignored.

@@

In the long term, increased regulation of the tech industry in general is inevitable, and regulation of encryption is
possible. Despite strong encryption's benefits, regulatory interest in the subject has not subdued. The form that
regulation will take in the field of encryption depends on the good faith efforts made to equitably balance all the
benefits and risks involved in deploying a cryptographic system. If the technical community acts, it can not only be
prepared for regulation, but lead and shape it.

Most importantly, in the pursuit of data privacy, regulatory action is part of the threat model. If the technical
community fails to act but regulators move forward, everyone may become subject to technically misguided laws that do
great harm. Bad \ac{EA} policy is just as much a threat as poor passwords.

For all these reasons, it is time that the technical community moves the debate forward.

@@

This paper accepts and builds on the following premises, some of which were introduced in \mysec{sec-motivation}. These
premises are not principles for potential \ac{EA} designs, but the starting place for discussing the \ac{EA} debate.

\eestart

\ee{The discussion must go on} As long as regulators continue pursuing \ac{EA} regulation, it is the responsibility of
the technical community to engage and respect the valid arguments being presented.

\ee{Cryptography is foundational} Strong cryptography in its various forms is foundational to digital security.

\ee{Investigators need data} The ability to access digital data for investigation and prosecution is important today and
will be increasingly important in the future.

\ee{Mass surveillance is a danger} Mass surveillance, which \ac{EA} makes easier, is a grave danger from which
representative governments are not immune.

\ee{Transparency is necessary} Transparency of the law enforcement and intelligence communities' data access capability
and usage is critical for public trust.

\ee{\Ac{EA} is an international problem} The internet is largely borderless, and international and human rights
considerations significantly constrain workable \ac{EA} solutions.

\ee{Perfection is not the goal} To loosely quote the ``insecurity axioms,'' insecurity cannot be destroyed, only moved
around \cite{nrc_schneider_1999}. \Ac{EA}, like all security, is a matter of finding the right balance of risk.

\eeend
